\subsection{Anharmonicity}
A series expansion of $\sum_{n,m}V(R_{n}-R_{m+n})$ to higher orders than the quadratic term gives anharmonic contributions. We look at the third-order term, which gives the first correction to the ideal boson gas picture.
\[\frac{1}{3!}\sum_{n,m}\underbrace{\frac{\partial^{3}V}{\partial x^{3}}\Bigg|_{x=R_{n}^{0}-R_{n+m}^{0}}}_{\Gamma(R_{n}^{0}-R_{n+m}^{0})=\Gamma(-R_{m}^{0})}\left(x_{n}-x_{n+m}\right)^{3}=\frac{1}{6}\sum_{m}\Gamma(-R_{m}^{0})\sum_{n}\left(x_{n}-x_{n+m}\right)^{3},\]
%where we used that $\sum_{m}\Gamma(-R^{0}_{m})=\sum_{m}\Gamma(R^{0}_{m})$.
Again we introduce the Fourier transforms of $x_{n}$, such that
\begin{align}
	\sum_{n}x_{n}^{3}=&\sum_{n}\left(\frac{1}{\sqrt{N}}\sum_{k_{1}}\tilde{x}_{k_{1}}e^{ik_{1}n}\right)\left(\frac{1}{\sqrt{N}}\sum_{k_{2}}\tilde{x}_{k_{2}}e^{ik_{2}n}\right)\left(\frac{1}{\sqrt{N}}\sum_{k_{3}}\tilde{x}_{k_{3}}e^{ik_{3}n}\right)\nonumber\\
	=&\frac{1}{\sqrt{N}}\sum_{k_{1},k_{2},k_{3}}\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{k_{3}}\underbrace{\frac{1}{N}\sum_{n}e^{i(k_{1}+k_{2}+k_{3})n}}_{\delta_{k_{1},-k_{2}-k_{3}}}\nonumber \\
	=&\frac{1}{\sqrt{N}}\sum_{k_{1},k_{2}}\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{-k_{1}-k_{2}}\nonumber,
\end{align}
while
\begin{align}
\sum_{n}x_{n}^{2}x_{n+m}=&\frac{1}{\sqrt{N}}\sum_{k_{1},k_{2}}\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{-k_{1}-k_{2}}e^{ik_{1}m},\nonumber
\end{align}
and by introducing $n'=n+m$ then
\begin{align}
	\sum_{n}x_{n}x_{n+m}^{2}=&\sum_{n'}x_{n'}^{2}x_{n'-m} \nonumber \\
	=&\frac{1}{\sqrt{N}}\sum_{k_{1},k_{2}}\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{-k_{1}-k_{2}}e^{-ik_{1}m}.\nonumber
\end{align}
Now the anharmonic third order term is
\begin{align}
	\frac{1}{6}\sum_{m}\Gamma(-R_{m}^{0})\sum_{n}(x_{n}-x_{n+m})^{3}&=\frac{1}{6}\sum_{m}\Gamma(-R_{m}^{0})\sum_{n}(x_{n}^{3}-x_{n+m}^{3}-3x_{n}^{2}x_{n+m}+3x_{n}x_{n+m}^{2})\nonumber \\ 
	&=\frac{1}{6}\sum_{m}\left(-\Gamma(-R_{m}^{0})\right)\sum_{k_{1},k_{2}}\frac{1}{\sqrt{N}}\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{-k_{1}-k_{2}}\left(e^{ik_{1}m}-e^{-ik_{1}m}\right)\nonumber\\
	&=\sum_{k_{1},k_{2}}M(k_{1})\tilde{x}_{k_{1}}\tilde{x}_{k_{2}}\tilde{x}_{-k_{1}-k_{2}},\nonumber \\
\end{align}
where
\begin{equation}
	M(k_{1})=\frac{-i}{3}\frac{1}{\sqrt{N}}\sum_{m}\Gamma(-R_{m}^{0})\sin(k_{1}m).\nonumber
\end{equation}
The anharmonic third order term can further be written
\begin{align}
\sum_{k_{1},k_{2}}M(k_{1})\left(\frac{\hbar}{2M}\right)^{\frac{3}{2}}\frac{1}{\sqrt{\omega_{k_{1}}\omega_{k_{2}}\omega_{k_{1}+k_{2}}}}\left(a^{\dagger}_{-k_{1}}+a_{k_{1}}\right)\left(a^{\dagger}_{-k_{2}}+a_{k_{2}}\right)\left(a^{\dagger}_{-k_{3}}+a_{k_{3}}\right)&=\nonumber \\
\sum_{k_{1},k_{2}}G(k_{1},k_{2})\Bigg(a^{\dagger}_{-k_{1}}a^{\dagger}_{-k_{2}}a^{\dagger}_{-q}+a^{\dagger}_{-k_{1}}a^{\dagger}_{-k_{2}}a^{\dagger}_{q}+a^{\dagger}_{-k_{1}}a_{k_{2}}a^{\dagger}_{-q}+a^{\dagger}_{-k_{1}}a^{\dagger}_{k_{2}}a_{q} \nonumber \\
+a_{k_{1}}a^{\dagger}_{-k_{2}}a^{\dagger}_{-q}+a_{k_{1}}a^{\dagger}_{-k_{2}}a_{q}+a_{k_{1}}a_{k_{2}}a^{\dagger}_{-q}+a_{k_{1}}a_{k_{2}}a_{q}\Bigg)\nonumber.
\end{align}
It is possible to do similar calculations for even higher order anharmonic terms.\newline
\newline
We notice that the number of phonons are not conserved in the scattering process resulting from the anharmonic term. However; \Underline{momentum is always conserved in all scattering processes!} \newline
\newline
Anharmonic effects are most important in crystals with small atom masses, $M$, and large lattice constants.\newline
\newline
We can generalize our method by looking at two- or three-dimensional lattices and introduce more than one mode, labelled by an index $\lambda$. For the \textit{harmonic} case we get
\[\Ha=\sum_{\B{q},\lambda}\hbar\omega_{\B{q},\lambda}\Creab_{\B{q},\lambda}\Annib_{\B{q},\lambda}.\]
Now the oscillations are described by vectors:
\[\B{x}_{\B{q},\lambda} =\sqrt{\frac{\hbar}{2M\omega_{\B{q},\lambda}}}\B{\xi}_{\B{q},\lambda}\left(\Creab_{-\B{q},\lambda}+\Annib_{\B{q},\lambda}\right), \]
\[\B{p}_{\B{q},\lambda}=i\sqrt{\frac{\hbar M\omega_{\B{q},\lambda}}{2}}\B{\xi}_{\B{q},\lambda}\left(\Creab_{\B{q},\lambda}-\Annib_{-\B{q},\lambda}\right),   \]
where $\B{\xi}_{\B{q},\lambda}$ is the excitation direction for mode $\lambda$ with wave vector $\B{q}$.

\subsection{Electron-phonon coupling}
Up to now we have looked at the second quantized form of the electron gas and lattice vibrations. We now want to couple these degrees of freedom. 
\[\Ha_{\mathrm{phonon}}=\sum_{\B{q},\lambda}\omega_{\B{q},\lambda}\Creab_{\B{q},\lambda}\Annib_{\B{q},\lambda},  \]
\[\Ha_{\mathrm{electron}}=\sum_{\B{k},\sigma}\vareps_{\B{k}}\Crea_{\B{k},\sigma}\Anni_{\B{k},\sigma}+\frac{1}{2}\sum_{\B{k},\B{k}',\B{q},\sigma,\sigma'}V(\B{q})\Crea_{\B{k},\sigma}\Crea_{\B{k}',\sigma'}\Anni_{\B{k}'+\B{q},\sigma'}\Anni_{\B{k}-\B{q},\sigma}  \]
Here we have used the plane wave representation for electrons, which is suitable for good metals. \newline
\newline
Earlier we looked at the second-quantized form of the one-particle operator 
\[H_{\mathrm{el-ion}} = \sum_{i}U(\B{r}_{i})=\sum_{i,j}V_{\mathrm{el-ion}}\left(\B{r}_{i};\B{R}_{j}\right)  \]
Previously we ignored the dynamics of the ion lattice when we second-quantized this term. When lattice excitations are included in $H_{\mathrm{el-ion}}$, this results in electron-phonon coupling.
\[V_{\mathrm{el-ion}}\left(\B{r}_{i};\B{R}_{j}\right)=V_{\mathrm{el-ion}}\left(\B{r}_{i}-\B{R}_{j}\right) \]
The equilibrium postion for lattice points are given by $\B{R}_{j}^{0}$, such that 
\[\B{R}_{j}=\B{R}_{j}^{0}-\sum_{\lambda}\B{x}_{j,\lambda}.  \]
The minus sign is just a convention which gives less minus signs in the calculations.\newline
\newline
We now write $V_{\mathrm{el-ion}}$ in a Taylor series in terms of small lattice excitations.We only use the lowest order term which has a non-zero contribution, and this is expected to be a good approximation for \textit{weak electron-phonon coupling}. The series is
\[V_{\mathrm{el-ion}}(\B{r}_{i}-\B{R}_{j})=V_{\mathrm{el-ion}}(\B{r}_{i}-\B{R}_{j}^{0})+\sum_{\lambda}\B{x}_{j,\lambda}\cdot\nabla V_{\mathrm{el-ion}}\Big|_{\B{r}_{i}-\B{R}_{j}^{0}}+... \] 
We have already looked at the first term, which results in
\[\Ha_{\mathrm{el-ion}}^{(1)}=\sum_{\B{k},\B{q},\sigma}\tilde{U}(\B{q})\Crea_{\B{k}+\B{q},\sigma}\Anni_{\B{k},\sigma} \]
where $\tilde{U}(\B{q})$ is the Fourier transform of $U(\B{r})=\sum_{j}V_{\mathrm{el-ion}}\left(\B{r}-\B{R}_{j}^{0}\right)$. This is the contribution from the \textit{static} ion lattice.\newline
\newline
We now look at
\[\sum_{i,j,\lambda}\B{x}_{j,\lambda}\cdot\nabla V_{\mathrm{el-ion}}(\B{r}_{i}-\B{R}_{j}^{0}),\]
and by introducing
\[V_{\mathrm{el-ion}}(\B{r})=\frac{1}{\sqrt{N}}\sum_{\B{q}}\tilde{V}_{\mathrm{e-i}}(\B{q})e^{i\B{q}\cdot\B{r}},\]
then
\[\nabla V_{\mathrm{el-ion}}=\frac{1}{\sqrt{N}}\sum_{\B{q}}i\B{q} \tilde{V}_{\mathrm{e-i}}(\B{q})e^{i\B{q}\cdot\B{r}}.
\]
We want to find the second-quantized form of the second term
\begin{align}
H_{\mathrm{el-ion}}^{(2)}=&\frac{1}{\sqrt{N}} \sum_{i,j,\lambda}\B{x}_{j,\lambda}\cdot\sum_{\B{q}}i\B{q}\tilde{V}_{\mathrm{e-i}}(\B{q})e^{i\B{q}\cdot(\B{r}_{i}-\B{R}_{j}^{0})}  \nonumber \\
=& \sum_{i}\sum_{\B{q},\lambda}\left(\frac{1}{\sqrt{N}}\sum_{j}\B{x}_{j,\lambda}e^{-i\B{q}\cdot\B{R}_{j}^{0}}\right)i\B{q}\tilde{V}_{\mathrm{e-i}}(\B{q})e^{i\B{q}\cdot\B{r}_{i}}\nonumber \\
=&\sum_{i}\sum_{\B{q},\lambda}\tilde{\B{x}}_{\B{q},\lambda}\cdot i\B{q}\tilde{V}_{\mathrm{e-i}}(\B{q})e^{i\B{q}\cdot\B{r}_{i}} \nonumber \\
\equiv&\sum_{i}F(\B{r}_{i})\nonumber ,
\end{align}
where
\[F(\B{r}_{i})=\sum_{q}\tilde{F}(\B{q})e^{i\B{q}\cdot\B{r}_{i}} \]
and 
\[\tilde{F}(\B{q})=\sum_{\lambda}\B{x}_{\B{q},\lambda}\cdot i\B{q}\tilde{V}_{\mathrm{e-i}}(\B{q}).     \]
When $H_{\mathrm{el-ion}}^{(2)}=\sum_{i}F(\B{r}_{i})$, we know that the second-quantized form in the plane wave basis is
\[\Ha_{\mathrm{el-ion}}^{(2)}=\sum_{\B{k},\B{q},\sigma}\tilde{F}(\B{q})\Crea_{\B{k}+\B{q},\sigma}\Anni_{\B{k},\sigma},   \]
since $F(\B{r})$ is independent of spin.\newline
\newline
We now introduce the quantized phonon-gas:
\[\B{x}_{\B{q},\lambda}=\sqrt{\frac{\hbar}{2M\omega_{\B{q},\lambda}}}\B{\xi}_{\B{q},\lambda}\left(\Creab_{-\B{q},\lambda}+\Annib_{\B{q},\lambda}\right) ,   \]
such that 
\[\tilde{F}(\B{q})=\sum_{\lambda}M_{\B{q},\lambda}\left(\Creab_{-\B{q},\lambda}+\Annib_{\B{q},\lambda}\right), \]
where\newline
\begin{center}
\boxed{M_{\B{q},\lambda}=i\left(\B{q}\cdot\B{\xi}_{\B{q},\lambda}\right)\sqrt{\frac{\hbar}{2M\omega_{\B{q},\lambda}}}\tilde{V}_{\mathrm{e-i}}(\B{q})   }
\end{center}
Finally,
\begin{align}
	\Ha_{\mathrm{el-ion}}=&\Ha_{\mathrm{el-phonon}} \nonumber \\
	=&\sum_{\B{k},\B{q},\sigma,\lambda}M_{\B{q},\lambda}\left(\Creab_{-\B{q},\lambda}+\Annib_{\B{q},\lambda}\right)\Crea_{\B{k}+\B{q},\sigma}\Anni_{\B{k},\sigma}.\nonumber
\end{align}
The quantity $M_{\B{q},\lambda}$ is the coupling constant between electrons and phonons. One important feature is that $M_{\B{q},\lambda}\propto\B{q}$, which means that
\begin{center}
	\boxed{\B{q}\rightarrow 0, \Rightarrow M_{\B{q},\lambda}\rightarrow 0.}
\end{center}
The case of $\B{q}=0$ is equivalent with that the whole lattice is translated uniformly, which does not affect the electrons due to Galilean invariance. \newline
\newline
Another important fact is that the coupling $M_{\B{q},\lambda}$ is independent of both $\B{k}$ and $\sigma$. The $\sigma$-independence comes naturally since the lattice potential is spin independent.  The coupling is independent of $k$ \Underline{only because we use the plane wave basis}. Also, $M_{\B{q},\lambda}\propto1/\sqrt{M}$, such that the coupling is weaker for heavy ions.
\section{Many-particle perturbation theory}
\subsection{Zero temperature}
Let us assume we can describe a system with a known Hamilton operator, for example
\[\Ha_{0}^{\mathrm{F}}=\sum_{\B{k},\sigma}\vareps_{\B{k}}\Crea_{\B{k},\sigma}\Anni_{\B{k},\sigma},\hspace{2.2cm}\mathrm{(fermions)} \] 
\[\Ha_{0}^{\mathrm{B}}=\sum_{\B{q},\lambda}\omega_{\B{q},\lambda}\Creab_{\B{q},\lambda}\Annib_{\B{q},\lambda}, \hspace{2cm}\mathrm{(bosons)} \]
and we want a description of the \textit{quantized} changes which happen as a result of perturbations of $\Ha_{0}$, i.e. $\Ha_{0}\rightarrow\Ha_{0}+V$. Usually, the perturbated Hamiltonian can not be diagonalized exactly.\\\newline
Examples of perturbations are:
\begin{enumerate}[i)]
	\item \[V=\sum_{\B{k},\B{q},\sigma,\lambda}M_{\B{q},\lambda}(\Creab_{-\B{q},\lambda}+\Annib_{\B{q},\lambda})\Crea_{\B{k}+\B{q},\sigma}\Anni_{\B{k},\sigma}\]
	\centerline{(Electron-phonon coupling)}	
	\item \[V=\sum_{\B{k},\B{k}',\B{q},\sigma,\sigma'}\tilde{V}(\B{q})\Crea_{\B{k},\sigma}\Crea_{\B{k}',\sigma'}\Anni_{\B{k}'+\B{q},\sigma'}\Anni_{\B{k}-\B{q},\sigma} \]
	\centerline{(Electron-electron interaction)}
	\item
	 The $U$-term in the Hubbard model.
\end{enumerate}
\subsection{Time-evolution of states}
Hamilton-operator \[\Ha=\Ha_{0}+V.\]
$\Ha_{0}$: One-particle operator. \newline
$V$: Perturbation, such that we can not solve the problem exact.
\begin{Indentskip}
	\subsubsection*{Schr\"odinger picture}
	\textit{Operators} are independent on time: $\hat{\mathcal{O}}(t)=\hat{\mathcal{O}}(0)$.\\
	\textit{States} are time-dependent: \[i\frac{\partial }{\partial t}|\psi\rangle =\Ha|\psi\rangle \]\newline
	Formally: \[|\psi(t)\rangle=e^{-i\Ha t}|\psi(0)\rangle  \] \newline
	$e^{-i\Ha t}$: Evolution operator which takes the system from the state $|\psi(0)\rangle$ at time $t=0$ to the state $|\psi(t)\rangle$ at time $t$.
\end{Indentskip}
\begin{Indentskip}
	\subsubsection*{Heisenberg picture}
	\textit{States} are time-independent: $|\psi(t)\rangle=|\psi(0)\rangle$.\\
	\textit{Operators} are time-dependent: \[\frac{d\hat{\mathcal{O}}}{dt} =-i\left[\hat{\mathcal{O}},\Ha\right]  \] \newline
	Formally: \[\hat{\mathcal{O}}(t)=e^{i\Ha t}\hat{\mathcal{O}}(0)e^{-i\Ha t}\] \newline
	Schr\"odinger: $\langle\psi(t)|\hat{\mathcal{O}}(0)|\psi(t)\rangle=\langle\psi(0)|e^{i\Ha t}\hat{\mathcal{O}}(0)e^{-i\Ha t}|\psi(0)\rangle$\newline
	Heisenberg:~ $\langle\psi(0)|\hat{\mathcal{O}}(t)|\psi(0)\rangle=\langle\psi(0)|e^{i\Ha t}\hat{\mathcal{O}}(0)e^{-i\Ha t}|\psi(0)\rangle$\newline
	\newline
	We get the same matrix elements in both pictures! \newline
\end{Indentskip}
There is a third picture, which is used in perturbation theory:
\subsubsection*{Interaction picture}
\begin{Indentskip}
	
	Some time-dependence in \textit{both} the states and the operators.
	\[|\psi(t)\rangle=e^{i\Ha_{0}t}e^{-i\Ha t}|\psi(0)\rangle,\]
	\[\hat{\mathcal{O}}(t)=e^{i\Ha_{0}t}\hat{\mathcal{O}}(0)e^{-i\Ha_{0}t}.\]
	
\end{Indentskip}
\Underline{NB:} In general, $\left[\Ha_{0},V\right]\neq0$, such that $e^{i\Ha_{0}t}e^{-i\Ha t}$ is much more complicated than $e^{-iVt}$!\newline
\newline
For $V=0$ the interaction picture coincides with the Heisenberg picture. Since we assume that the components of $V$ is much smaller than the components of $\Ha_{0}$ for the perturbation theory to work, it follows that most of the time development lies in the operators, while the states has a slow time-variation. \newline
\newline
\textbf{\Underline{Evolution operator for a state $|\psi(t)\rangle$ in the interaction picture:}}\newline
\begin{align}
	|\psi(t)\rangle &= U(t)|\psi(0)\rangle,\nonumber \\
U(t)&=e^{i\Ha_{0}t}e^{-i\Ha t}\neq e^{i(\Ha_{0}-\Ha_{0}-V)t} ~~(!!)\nonumber
\end{align}
\newline
\boxed{V=0 : \\
U(t)=. \left[\Ha_{0},\Ha_{0}\right]=.  e^{i\Ha_{0}t}e^{-i\Ha_{0}t}=1. } \newline
\newline
$U(t)$ have a non-trivial time-dependence only when $V\neq0$, and we want to find $U$ as a functional of $V$. (A functional is a number which depends on a function, i.e. a mapping from a space of functions onto the complex numbers.)\newline
\newline
We find $U(t)$ from $V(t)$ like this: \newline
\begin{align}
	\frac{\partial U}{\partial t} =&~~ \frac{\partial}{\partial t}\left(e^{i\Ha_{0}t}e^{-i\Ha t}\right)\nonumber \\
	=&~~ i\Ha_{0}e^{i\Ha_{0}t}e^{-i\Ha t}-e^{i\Ha_{0}t}i\Ha e^{-i\Ha t} \nonumber \\
	=&~~ ie^{i\Ha_{0}t}\left(\Ha_{0}-\Ha \right)e^{-i\Ha t} \nonumber \\
	=&~~ ie^{i\Ha_{0}t}Ve^{-i\Ha t}\nonumber \\ 
	=& -i\underbrace{e^{i\Ha_{0}t}Ve^{-i\Ha_{0}t}}_{\hat{V}(t)}\underbrace{e^{i\Ha_{0}t}e^{-i\Ha t}}_{U(t)}\nonumber \\
	=&-i\hat{V}(t)U(t).\nonumber 
\end{align}
$\hat{V}(t)$ explisitly time-dependent, such that $U(t)\neq e^{-i\hat{V}t}U(0)$. \newline
\newline
When $V=0$ then $\partial U/\partial t=0$, such that $U(t)=U(0)=1$.\newline
\newline
We integrate over $t$:
\begin{align}
	\int_{0}^{t}dt'\frac{\partial U(t')}{\partial t'}&=U(t)-U(0)\nonumber \\ 
	&= -i\int_{0}^{t}dt'\hat{V}(t')U(t'),
\end{align}
such that \newline
\begin{center}
		\boxed{U(t)=1-i\int_{0}^{t}dt'\hat{V}(t')U(t')}
			\end{center}
\vspace{5pt}
This is a (linear) integral equation for $U(t)$. We want to solve this by iteration, but first we introduce a more general evolution operator.
\subsubsection*{The $S$-matrix}
The scattering matrix, $S$, is the central quantity in many-particle perturbation theory. With a perturbation theory for $S$ then we will almost automatically have a method to write a perturbation series for \textbf{\Underline{any physical quantity}}. The $S$-matrix is defined as:
\[|\psi(t)\rangle=S(t,t')|\psi(t')\rangle,\] such that
$S(t,0)=U(t),$ by recalling that $|\psi(t)\rangle = U(t)|\psi(0)\rangle$. The state can be written as
\begin{align}
	|\psi(t)\rangle&=S(t,t')|\psi(t')\rangle\nonumber \\
	&=S(t,t')U(t')|\psi(0)\rangle, \nonumber
\end{align}
such that 
\[U(t)=S(t,t')U(t'),\]
or in other words
\[S(t,t')=U(t)U^{-1}(t').\]
We utilize the unitarity of $U$, which we find from
\[U^{-1}(t)=e^{i\Ha t}e^{-i\Ha_{0}t}=U^{\dagger}(t),\] 
such that the scattering matrix is written as
\begin{center}
	\boxed{S(t,t')=U(t)U^{\dagger}(t').}
\end{center}
We want to find an integral equation for $S$:
\begin{align}
	\frac{\partial S(t,t')}{\partial t} &= \frac{\partial U(t)}{\partial t}U^{\dagger}(t')\nonumber \\
	&= -i\hat{V}(t)U(t)U^{\dagger}(t')\nonumber \\
	&= -i\hat{V}(t)S(t,t'). \nonumber
\end{align}
We integrate over time: 
\begin{align}
	\int_{\tilde{t}}^{t}\frac{\partial S(t'',t')}{\partial t''} =& S(t,t')-S(\tilde{t},t') \nonumber \\
	=&-i\int_{\tilde{t}}^{t}dt''\hat{V}(t'')S(t'',t').
\end{align}
In the special case of $\tilde{t}=t'$, then $S(t',t')=1=U(t')U^{\dagger}(t')$. The integral equation for the scattering matrix then follows:
\begin{center}
	\boxed{S(t,t')=1-i\int_{t'}^{t}dt''\hat{V}(t'')S(t'',t')}
\end{center}
The time evolution of $S$ is given by $\hat{V}(t)=e^{i\Ha_{0}t}Ve^{-i\Ha_{0}t}$, and in a similar way as for $U(t)$ we can construct a perturbation theory for $S(t,t')$ by solving the integral equation by iteration.\newline
\newline
\Underline{0'th approx.:} 
\[S_{0}(t,t')=1.\]
\Underline{1st approx.:}
\[S_{1}(t,t')=1-i\int_{t'}^{t}dt''\hat{V}(t'').\]
Now we can see what it means that $V$ should be small, i.e. \[\left|\int_{t'}^{t}dt''\hat{V}(t'')\right|\ll1.\]
\begin{Indentskip}
	\subsubsection*{Properties of the $S$-matrix:}
	\[S(t,t)=1,\]
	\begin{align}
		\left(S(t,t')\right)^{\dagger}&=\left(U(t)U^{\dagger}(t')\right)^{\dagger} = U(t')U^{\dagger}(t)\nonumber \\
	&=S(t't),\nonumber
	\end{align}
	\[S(t,t'')=S(t,t')S(t',t''),\] since
	\begin{align}
		|\psi(t)\rangle&=    \nonumber
	\end{align}
\end{Indentskip}
To find an exact expression for $S$ we introduce the \Underline{time ordering operator}: $\tilde{T}$.
\subsection*{Time ordering of operators}
\Underline{Bosons:}\newline
Two boson operators have time-ordered product 
\[\tilde{T}[A(t_{1})B(t_{2})]= \begin{cases}A(t_{1})B(t_{t}); & t_{1}>t_{2}.\\
B(t_{2})A(t_{1}); & t_{2}>t_{1}.
\end{cases} \]
\newline
\Underline{Fermions:}\newline
Two fermion operators have time-ordered product
\[\tilde{T}[A(t_{1})B(t_{2})]= \begin{cases}A(t_{1})B(t_{t}); & t_{1}>t_{2}.\\
-B(t_{2})A(t_{1}); & t_{2}>t_{1}.
\end{cases} \] \newline
The operator $\tilde{T}$ orders the operator with the earliest time to the right, such that it operates first on a ket, $|\psi\rangle$.\newline
\newline
We look further at the equation for $S$:
\[S(t,t')=1-i\int_{t'}^{t}dt''\hat{V}(t'')S(t'',t'),\]
\Underline{0.:}\newline
\[S_{0}(t,t')=1,\]
\Underline{1.:}\newline
\[S_{1}(t,t')=1-i\int_{t'}^{t}dt''\hat{V}(t''),\]
\Underline{2.:}\newline
\begin{align}
	S_{2}(t,t')&=1-i\int_{t'}^{t}dt''\hat{V}(t'')S_{1}(t'',t')\nonumber \\
	&=1-i\int_{t'}^{t}dt''\hat{V}(t'')\left(1-i\int_{t'}^{t''}dt'''\hat{V}(t''')\right) \nonumber \\ 
	&=1+(-i)\int_{t'}^{t}dt''\hat{V}(t'')+(-i)^{2}\int_{t'}^{t}dt''\int_{t'}^{t''}dt'''\hat{V}(t'')\hat{V}(t'''),\nonumber
\end{align}
This can be done infinitly, such that
\[S(t,t')=1+\sum_{n=1}^{\infty}(-i)^{n}\int_{t'}^{t}dt_{1}\int_{t'}^{t_{1}}dt_{2}...\int_{t'}^{t_{n-1}}dt_{n}\left(\hat{V}(t_{1})\hat{V}(t_{2})...\hat{V}(t_{n})\right).\]
This expression is such that all the integrations have the same lower bound, $t'$, while the upper bounds are different. We use time ordering of the operators to get all the upper integration bounds the same.\newline
\newline
Let us consider a $\hat{V}$ consisting of a combination of fermion and/or boson operators in a way such that 
\[\tilde{T}\left[V(t_{1})V(t_{2})\right]=\begin{cases}
V(t_{1})V(t_{2}); & t_{1}>t_{2} \\
V(t_{2})V(t_{1}); & t_{2}>t_{1}. \end{cases}\]
We then look at the expression
\begin{align}
	\frac{1}{2!}\int_{t'}^{t}dt_{1}\int_{t'}^{t}dt_{2}\tilde{T}\left[\hat{V}(t_{1})\hat{V}(t_{2})\right] =&~~~ \frac{1}{2}\int_{t'}^{t}dt_{1}\int_{t'}^{t_{1}}dt_{2}\hat{V}(t_{1})\hat{V}(t_{2}) \nonumber \\
	&+\frac{1}{2}\int_{t'}^{t}dt_{2}\int_{t'}^{t_{2}}dt_{1}\hat{V}(t_{2})\hat{V}(t_{1}) \nonumber \\
	=& \int_{t'}^{t}dt_{1}\int_{t'}^{t_{1}}dt_{2}\hat{V}(t_{1})\hat{V}(t_{2}),
\end{align}
by interchanging the labels $t_{1}\leftrightarrow t_{2}$ in the second term.\newline
\newline
In the same way:
\[\frac{1}{n!}\int_{t'}^{t}dt_{1}\int_{t'}^{t}dt_{2}...\int_{t'}^{t}dt_{n}\tilde{T}\left[\hat{V}(t_{1})...\hat{V}(t_{n})\right]=\int_{t'}^{t}dt_{1}\int_{t'}^{t_{1}}dt_{2}...\int_{t'}^{t_{n-1}}dt_{n}\hat{V}(t_{1})...\hat{V}(t_{n}).\]
We then get an expression for $S$:
\begin{align}
	S(t,t')&=1+\sum_{n=1}^{\infty}\frac{(-i)^{n}}{n!}\int_{t'}^{t}dt_{1}...\int_{t'}^{t}dt_{n}\tilde{T}\left[\hat{V}(t_{1})...\hat{V}(t_{n})\right]\nonumber \\
	&=1+\tilde{T}\sum_{n=1}^{\infty}\frac{(-1)^{n}}{n!}\left[\int_{t'}^{t}dt''\hat{V}(t'')\right]^{n},
\end{align}
which can be written formally as 
\begin{center}
	\boxed{S(t,t')=\tilde{T}\left[\exp\left(-i\int_{t'}^{t}dt''\hat{V}(t'')\right)\right]}
\end{center}
	Typically, we want to calculate expectation values on the form
	\[\langle\psi(0)|\hat{O}(t)|\psi(0)\rangle.\]
	Here, the state $|\psi(0)\rangle$ is the exact ground state for the interacting system. The problem is that $|\psi(0)\rangle$ is unknown, since $\Ha=\Ha_{0}+V$ is such that we cannot solve the problem exact. Can we relate $|\psi(0)\rangle$ formally to the groundstate $|\phi\rangle_{0}$ of $\Ha_{0}$? \newline
	\newline
	The Gell-Mann-Low relations solves this. The trick is to introduce the perturbation $V$ adiabatically, i.e. the potential is turned on really slowly. We can use 
	\[\Ha = \Ha_{0}+Ve^{-|t|\epsilon},\]
	where $\epsilon$ is very small, and we assume that we study the system for times $|t|\ll\epsilon$.